An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-03-09 tex/paper.tex
Minor changes
- Fix grammatical error in sentence.
- Quick indication as to what tournament type means.
- Adding the fact that we can have the full tournament interactions.

\begin{table}[!hbtp]
    \begin{center}
        \begin{tabular}{ccccc}
            \toprule
            Year     & Reference                  & Number of Strategies & Type     & Source Code\\
            \midrule
            1979     & \cite{Axelrod1980a}        & 13                   & Standard & Not immediately available\\
            1979     & \cite{Axelrod1980b}        & 64                   & Standard & Available in FORTRAN\\
            1991     & \cite{Bendor1991}          & 13                   & Noisy    & Not immediately available\\
            2002     & \cite{Stephens2002}        & 16                   & Wildlife & Not applicable\\
            2005     & \cite{kendall2007iterated} & 223                  & Varied   & Not available \\
            2012     & \cite{Stewart2012}         & 13                   & Standard & Not fully available \\
            \bottomrule
        \end{tabular}
    \end{center}
    \caption{An overview of published tournaments (specify what "type" means)}\label{tab:tournaments}
\end{table}

@@

Due to the open nature of the library the number of strategies included has
grown at a fast pace, as can be seen in
Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
previous research being done in an irreproducible manner, with for example no
source code, and/or vaguely described strategies, not all previous tournaments
are yet to be reproduced. In fact, some of the early tournaments might be
impossible to reproduce as the source code is forever lost, and this library aims
to prevent this from happening again in the future.

@@

\begin{itemize}
    \item Noisy tournaments;
    \item Ecological analysis of tournaments;
    \item Morality metrics based on \cite{Singer-Clark2014};
    \item Transformation of strategies (in effect giving an infinite number of
        strategies);
    \item Classification of strategies according to multiple dimensions.
\end{itemize}

These capabilities are constantly being updated. Some immediate further work
includes allowing for tournaments of probabilistic length as well as further
implementation of known strategies

>>>>

\begin{table}[!hbtp]
    \begin{center}
        \begin{tabular}{ccccc}
            \toprule
            Year     & Reference                  & Number of Strategies & Type     & Source Code\\
            \midrule
            1979     & \cite{Axelrod1980a}        & 13                   & Standard & Not immediately available\\
            1979     & \cite{Axelrod1980b}        & 64                   & Standard & Available in FORTRAN\\
            1991     & \cite{Bendor1991}          & 13                   & Noisy    & Not immediately available\\
            2002     & \cite{Stephens2002}        & 16                   & Wildlife & Not applicable\\
            2005     & \cite{kendall2007iterated} & 223                  & Varied   & Not available \\
            2012     & \cite{Stewart2012}         & 13                   & Standard & Not fully available \\
            \bottomrule
        \end{tabular}
    \end{center}
    \caption{An overview of a selection of published tournaments. Not all
             tournaments were `standard' round robins; for more details
             see the indicated references.}\label{tab:tournaments}
\end{table}

@@

Due to the open nature of the library the number of strategies included has
grown at a fast pace, as can be seen in
Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
previous research being done in an irreproducible manner, with for example no
source code, and/or vaguely described strategies, not all previous tournaments
are yet to be reproduced. In fact, some of the early tournaments might be
impossible to reproduce as the source code is forever lost. This library aims
to prevent this from happening again in the future.

@@

\begin{itemize}
    \item Noisy tournaments;
    \item Ecological analysis of tournaments;
    \item Morality metrics based on \cite{Singer-Clark2014};
    \item Transformation of strategies (in effect giving an infinite number of
        strategies);
    \item Classification of strategies according to multiple dimensions.
    \item Gathering of full interaction history for all interactions.
\end{itemize}

These capabilities are constantly being updated. Some immediate further work
includes allowing for tournaments of probabilistic length as well as further
implementation of known strategies.
